### 2023-03-13 source/paper/main.tex
Add years of 1986 CPS data, event study
Fixing models
Normalize arrest rate, fix outcome var
Fix AB event study

\begin{itemize}[itemsep=0.05mm, parsep=0pt]
  \item CPS October supplement
  \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
  \item ACS
\end{itemize}

@@

@@

\begin{figure}[h]
  \caption{Event study 1986, AB arrest rate 18F}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
  \label{fig:TBD}
\end{figure}

@@

\begin{figure}[h]
  \caption{Event study 2010, AB arrest rate 18F}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
  \label{fig:TBD}
\end{figure}

>>>>

\begin{itemize}[itemsep=0.05mm, parsep=0pt]
  \item CPS October supplement
  \begin{itemize}
    \item Dropped observations with missing family income data
  \end{itemize}
  \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
  \begin{itemize}
    \item Arrest data normalized to state population data. State population data are based on U.S. Census Bureau midyear population estimates.
  \end{itemize}
  \item ACS
\end{itemize}

@@

\textbf{Basic event study model}
\begin{equation} \label{eq:1}
  y_{it} = \alpha_i + \gamma_t + q'_{it} \phi + \sum_{m=-G}^{M} \beta_m z_{i,t-m} + C_{it} +\epsilon_{it}
\end{equation}

where $\alpha_i$ and $\gamma_t$ are individual and time fixed effects,

@@

\begin{figure}[h]
  \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Black Men}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
  \label{fig:ab_es_1986}
\end{figure}

\begin{footnotesize}
  \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992. Event time $0 \coloneqq 1986$. The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 1984. The sample is defined as black males aged 18-24 in 1986 who are not currently incarcerated. Control variables include population and unemployment rates at the state-year level. 
\end{footnotesize}

@@

\begin{figure}[h]
  \caption{Effect of Fair Sentencing Act on Drug-related Arrest Rate of Black Men}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
  \label{fig:ab_es_2010}
\end{figure}

\begin{footnotesize}
  \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:1} evaluating the impact of the Fair Sentencing act of 2010 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 2005-2015. Event time $0 \coloneqq 2010$. The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high-drug arrest states are defined to be those above the 75th percentile in 2008. The sample is defined as black males aged 18-24 in 2010 who are not currently incarcerated. Control variables include population and unemployment rates at the state-year level. 
\end{footnotesize}
